Nail: A practical interface generator for data formats

### 2014-12-03 paper/login/design.tex
make spell

Just like C supports various constructs to build up types, such as structures and unions from pointers and
elemental types, Nail supports various \emph{combinators} to represent features of a file or protocol. We will present the features we used in implementing
DNS. A more complete reference can be found in Figure~\ref{fig:syntax}, with detailed rationale in~\cite{bangert:nail}.

@@

The body of the \texttt{dnspacket} rule is a structure, which contains any number of fields enclosed
between  curly braces. Each field in the structure is parsed in sequence, and represented as a
structure to the programmer.  Contrary to other programming languages, Nail does not have a special
keyword for structs. We also reverse the usual structure-field syntax: \texttt{id uint1} is a field
called \texttt{id} with type \texttt{uint1}. Often, Nail grammars have
structures with just one non-constant field, for example when parsing a fixed header. Nail supports
this with an alternative form of structures,
using angle brackets, that contains one unnamed, non-constant field, which is represented directly
in the datatype, without introducing another layer of indirection, as shown on line 40.

@@

\subsection{Redundant Data}
\label{s:dependent}
Data formats often contain values that are determined by other values or the layout of information,
such as checksums, duplicated information, or offset and  length fields. Exposing such values risks
inconsistencies that could trick the program into unsafe behaviour. Therefore, we represent such values using \emph{dependent fields} and handle them transparently during
parsing and generation without exposing them to the application. 
Dependent fields are handled like other fields when parsing input, but only stored temporarily
instead of in the data type. Their value can be referenced by other parsers until it goes out of scope.
When generating output, Nail inserts the correct value.

>>>>

Just like C supports various constructs to build up types, such as structures and unions from pointers and
elemental types, Nail supports various \emph{combinators} to represent features of a file or protocol. We will present the features we used in implementing
DNS\@. A more complete reference can be found in Figure~\ref{fig:syntax}, with detailed rationale in~\cite{bangert:nail}.

@@

The body of the \texttt{dnspacket} rule is a structure, which contains any number of fields enclosed
between  curly braces. Each field in the structure is parsed in sequence, and represented as a
structure to the programmer.  Contrary to other programming languages, Nail does not have a special
keyword for structs. We also reverse the usual structure-field syntax: \texttt{id uint1} is a field
called \texttt{id} with type \texttt{uint1}. Often, Nail grammars have
structures with just one non-constant field, for example when parsing a fixed header. Nail supports
this with an alternative form of structures,
using angle brackets, that contains one unnamed, non-constant field, which is represented directly
in the data type, without introducing another layer of indirection, as shown on line 40.

@@

\subsection{Redundant Data}
\label{s:dependent}
Data formats often contain values that are determined by other values or the layout of information,
such as checksums, duplicated information, or offset and  length fields. Exposing such values risks
inconsistencies that could trick the program into unsafe behavior. Therefore, we represent such values using \emph{dependent fields} and handle them transparently during
parsing and generation without exposing them to the application. 
Dependent fields are handled like other fields when parsing input, but only stored temporarily
instead of in the data type. Their value can be referenced by other parsers until it goes out of scope.
When generating output, Nail inserts the correct value.

### 2014-12-03 paper/login/eval.tex
sync n*.bib
make spell

\paragraph{DNS} In Section~\ref{s:design}, we introduced Nail's syntax with a grammar
for DNS packets, shown in Figure~\ref{fig:dns-full}.
The grammar corresponds almost directly to the diagrams in RFC 1035,
which defines DNS. Nail's dependent fields handle DNS's count fields, and
transformations represent label compression. Both of these features are awkward at best to handle
with existing tools.

@@

\paragraph{DNS.}

@@

To evaluate whether Nail-based parsers are compatible with good
performance, we compare the performance of our DNS server to that of ISC
BIND 9 release 9.9.5, a mature and widely used DNS server.
We simulate a load resembling that of an authoritative name server, generating a random zone file
and a random sequence of queries, with 10\% non-existent domains. We repeated this sequence of
queries for one minute against both DNS servers. We found that our DNS server is approximately three
times faster than BIND. Although BIND is a more sophisticated DNS server,
and implements many features that are not present in our Nail-based DNS
server and that allow it to be used in more complicated configurations, 
we believe our results demonstrate that Nail's parsers are not
a barrier to achieving good performance.
\paragraph{ZIP.}

@@

In our full paper~\cite{bangert:nail-osdi14}, we present a study of 15 ZIP parsing bugs.
11 of these vulnerabilities involved memory corruption during input handling, which generated code
is immune to by design. We also fuzz-tested our DNS server.
More interestingly, Nail also protects against parsing inconsistency vulnerabilities like the four others we studied.
Nail grammars explicitly encode duplicated information such as the redundant length fields in ZIP
that caused a vulnerability in the Python ZIP library. The other three vulnerabilities exist
because multiple implementations of the same protocol disagree on some inputs. Hand-written protocol
parsers are not very reusable, as they build application-specific data structures and are tightly
coupled to the rest of the code. Nail grammars, however, can be re-used between applications,
avoiding protocol misunderstandings.

>>>>

\paragraph{DNS} In Section~\ref{s:design}, we introduced Nail's syntax with a grammar
for DNS packets, shown in Figure~\ref{fig:dns-full}.
The grammar corresponds almost directly to the diagrams in RFC 1035,
which defines DNS\@. Nail's dependent fields handle DNS's count fields, and
transformations represent label compression. Both of these features are awkward at best to handle
with existing tools.

@@

\paragraph{DNS\@.}

@@

To evaluate whether Nail-based parsers are compatible with good
performance, we compare the performance of our DNS server to that of ISC
BIND 9 release 9.9.5, a mature and widely used DNS server.
We simulate a load resembling that of an authoritative name server, generating a random zone file
and a random sequence of queries, with 10\% non-existent domains. We repeated this sequence of
queries for one minute against both DNS servers. We found that our DNS server is approximately three
times faster than BIND\@. Although BIND is a more sophisticated DNS server,
and implements many features that are not present in our Nail-based DNS
server and that allow it to be used in more complicated configurations, 
we believe our results demonstrate that Nail's parsers are not
a barrier to achieving good performance.
\paragraph{ZIP\@.}

@@

In our full paper~\cite{bangert:nail}, we present a study of 15 ZIP parsing bugs.
11 of these vulnerabilities involved memory corruption during input handling, which generated code
is immune to by design. We also fuzz-tested our DNS server.
More interestingly, Nail also protects against parsing inconsistency vulnerabilities like the four others we studied.
Nail grammars explicitly encode duplicated information such as the redundant length fields in ZIP
that caused a vulnerability in the Python ZIP library. The other three vulnerabilities exist
because multiple implementations of the same protocol disagree on some inputs. Hand-written protocol
parsers are not very reusable, as they build application-specific data structures and are tightly
coupled to the rest of the code. Nail grammars, however, can be re-used between applications,
avoiding protocol misunderstandings.
